---
title: "Data-Scientific Programming: Assignment 2"
author: "Your Name"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```


### Directions: Refer to [sections 3.1-3.10 in R for Data Science](https://r4ds.had.co.nz/data-visualisation.html), and the Data Graphics Notes.

### Upload the html file containing your code and answers to Moodle. 

We'll start by loading the tidyverse package. 

```{r}
library(tidyverse)
```

In this assignment, we will continue to use the `mpg` dataset, referenced in the book. This dataset is automatically loaded with the `tidyverse` package. 


## Question 1

### Section 3.5 describes how to use faceting in graphs. Experiment with the commands shown in the section, and in Exercise 3.5.1. Write a paragraph summarizing your results. Your paragraph should address all of the following:

* What is the difference between faceting on one variable (i.e. `~ class`), compared with two variables (i.e. drv ~ cyl)?    
* When is it useful to use in `.` faceting?   
* What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages?     
* What happens if you facet on a continuous variable, such as `displ`?

### You are welcome to include plots in your response, but this is not required. 

Type paragraph here. 
1) For faceting on one variable we need to use facet_wrap(), and with two variables we need to use facet_grid()
2) To not facet in rows and columns dimensions
3) I think as an advantage, it is helpful to see separate graphs with only one certain data in it, depending on what a programmer is looking for to be shown. Which could be  a disadvantage if a programmer needs a bigger picture of more data in the single graph.
4) You will get one row or column for each unique value of the variable.  

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2) 
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```


## Question 2

### Write code to recreate all six of the plots in Exercise 3.6.1, question 6. 

Plot 1:

```{r}
#Type code here
```

Plot 2:

```{r}
#Type code here
```

Plot 3:

```{r}
#Type code here
```

Plot 4:

```{r}
#Type code here
```

Plot 5: 

```{r}
#Type code here
```

Plot 6: 

```{r}
#Type code here
```

## Question 3

### Create a bar graph displaying number of cars of each class `class`. Order the bars in descending order by height. 

```{r}
#Type code here
```

## Question 4

### Create a stacked bar graph displaying class along the x-axis, and using the `fill` argument to show the number of cars of each drive type `drv`, (4=four wheel drive, f=front wheel drive, r=rear wheel drive), for each class of cars. Briefly summarize your findings. 

```{r}
#Type code here
```

Type summary here. 

## Question 5

### The following code creates a new dataset, called `mpg_classes`, that displays the average highway mpg for each class of car. 

```{r}
mpg_classes <- mpg %>% group_by(class) %>% 
  summarize(Avg_hwy = mean(hwy))
```

### We display the dataset below. 

```{r}
mpg_classes
```


### Create a bar graph with each class of vehicle on the x-axis, and `Avg_hwy` on the y-axis. Order the bars in descending order of heights. 

```{r}
#Type code here
```
